\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1:} #2 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
  {\LARGE \textbf{Pulkit Singh}}\\
  \vspace{0.5em}
  \href{mailto:pulkitsinghmail@gmail.com}{pulkitsinghmail@gmail.com} \quad | \quad +91-6294872159 \\
  \href{https://www.linkedin.com/in/pulkit5ingh/}{linkedin.com/in/pulkit5ingh} \quad | \quad \href{https://github.com/pulkit5ingh}{github.com/pulkit5ingh}
\end{center}

\section{Professional Summary}
Results-driven Backend Engineer with over 5 years of experience designing and developing scalable, high-performance APIs and backend infrastructures using Node.js, NestJS, and MongoDB. Skilled in microservices architecture, third-party integrations, and cloud deployments. Adept at collaborating with cross-functional teams and delivering business-critical solutions in foodtech, travel, healthcare, and marketplaces.

\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Languages}{JavaScript, TypeScript}
  \resumeSubItem{Frameworks \\& Libraries}{Node.js, Express.js, NestJS, React.js, Next.js}
  \resumeSubItem{Databases}{MongoDB, PostgreSQL}
  \resumeSubItem{DevOps \\& Tools}{AWS (S3, EC2), Docker, Redis, Git, PM2, Nginx, BullMQ, DigitalOcean}
  \resumeSubItem{Practices}{RESTful APIs, Microservices, CI/CD, Agile, Swagger, Postman, RBAC, Webhooks}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Senior Backend Engineer - Corpusvision Technologies Pvt. Ltd.}{Feb 2023 -- Present}
  {Mumbai, Maharashtra (Hybrid)}{}
  \resumeItemListStart
    \resumeItem{Backend Architecture}
      {Designed and developed robust APIs for platforms like Travelbaba, Quiksale, Ordercoro, and Treint using NestJS and TypeScript.}
    \resumeItem{Role-Based Access Control (RBAC)}
      {Implemented scalable RBAC system using PassportJS and JWT, enabling dynamic permission management.}
    \resumeItem{Bulk Upload System}
      {Built an Excel-based bulk upload engine with validation, transformation, and feedback mechanisms using BullMQ and Redis.}
    \resumeItem{Analytics \\& Reporting}
      {Leveraged MongoDB aggregation pipelines to generate real-time admin and user reports.}
    \resumeItem{Payment Gateway Integrations}
      {Integrated Razorpay, PhonePe, and Easebuzz via webhooks, supporting subscriptions and transactional workflows.}
    \resumeItem{PDF \\& Notification Automation}
      {Automated generation of OTPs, invoices, and quotations with templated PDFs and multi-channel notifications (Email/SMS).}
    \resumeItem{Infrastructure Management}
      {Managed deployments with Docker, PM2, and Nginx. Configured AWS S3 for secure file handling and CI/CD pipelines.}
  \resumeItemListEnd

\resumeSubheading
  {Backend Engineer - DandD Tech USA Inc.}{Oct 2020 -- Jan 2023}
  {Brooklyn, NY (Remote)}{}
  \resumeItemListStart
    \resumeItem{API Development}
      {Delivered scalable REST APIs for Robofood (restaurant SaaS) and Frontliner (healthcare EMR) using Express.js and MongoDB.}
    \resumeItem{Module Design}
      {Implemented modules for POS, inventory, delivery, booking, and order tracking.}
    \resumeItem{Automation}
      {Scheduled CRON jobs for reporting and user alerts.}
    \resumeItem{Authentication}
      {Enabled secure login via Firebase Auth and Twilio for OTP-based access.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
  \resumeSubItem{TravelBaba.ai \href{https://travelbaba.ai}{travelbaba.ai}}
    {AI-based travel planning platform integrated with Claude AI (Anthropic SDK). Ensured structured output via strict JSON schema validation for itineraries and hotel data.}
  \resumeSubItem{Quiksale \href{https://quiksale.in}{quiksale.in}}
    {Local product resale marketplace with SEO-friendly category-location URLs, referral tracking, and subscription management. Built using NestJS and MongoDB.}
  \resumeSubItem{Tripinnov \href{https://tripinnov.com}{tripinnov.com}}
    {SaaS solution for travel agents to manage itineraries, dynamic pricing, and commissions.}
  \resumeSubItem{Ordercoro \href{https://ordercoro.com}{ordercoro.com}}
    {Multi-role foodtech ecosystem supporting vendors, restaurants, and logistics. Built with RBAC and webhook-based order flows.}
  \resumeSubItem{Robofood \href{https://robofood.io}{robofood.io}}
    {POS-enabled cloud kitchen automation suite with inventory, billing, and delivery modules.}
  \resumeSubItem{Frontliner \href{https://frontliner.care}{frontliner.care}}
    {End-to-end EMR and staffing platform connecting patients and caregivers.}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Institute of Science and Technology}{2017 -- 2020}
    {Bachelor of Computer Applications (BCA)}{Chandrakona, West Bengal}
  \resumeSubheading
    {S.E. Rly Mixed Higher Secondary School (English Medium)}{2012 -- 2017}
    {Higher Secondary and Secondary}{Kharagpur, West Bengal}
\resumeSubHeadingListEnd

\end{document}
