%-------------------------
% Resume in Latex
% Author : pulkit Singh
% Website: https://github.com/pulkit5ingh
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://pulkitsingh.vercel.app/}{\Large Pulkit Singh}} & Email : \href{mailto:pulkitsinghmail@gmail.com}{pulkitsinghmail@gmail.com}\\
  \href{https://pulkitsingh.vercel.app/}{https://www.pulkitsingh.vercel.app/} & Mobile : +91-6294872159 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Institute Of Science and Technology}{Chandrakona West Bengal}
    {Master of Computer Applications}{2020 -- 2022}
    \resumeSubheading
    {Institute Of Science and Technology}{Chandrakona West Bengal}
    {Bachelor of Computer Applications}{2017 -- 2020}
    \resumeSubheading
    {S.E Rly Mixed Higher Secondary School ( English Medium )}{Kharagpur West Bengal}
    {Secondary and Higher Secondary}{2012 -- 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Corpusvision Technologies Pvt. Ltd.}{Bhandup West, Mumbai, Maharashtra}
  {Senior Backend Engineer}{February 2023 - Present}
  \resumeItemListStart
  \resumeItem{Projects}
       {Built and Engineered backend APIs for multiple projects such as
       \href{https://tripinnov.com/}{https://tripinnov.com/} - A tech travel platform for common travel agents.
       \href{https://www.ordercoro.com/}{https://www.ordercoro.com/} - India’s leading food tech platform for hyper-local market.
       }
  \resumeItem{Authentication and Authorization}
      {Integrated Secure Authentication and Authorization: Using Twilio Verify V2 Service for OTP authentication and verification, along with jsonwebtoken , PassportJS.}
  \resumeItem{Notification Service}
      {Integrated notifications services for email using Twilio with send grid api along with Node mailer, and for SMS Twilio SMS and whatsapp massaging service along with Test Local API}
  \resumeItem{Payment gateways}
      {I utilized PhonePe's and Easebuzz payment gateway API with webhooks to facilitate seamless money transactions.}
  \resumeItem{Documentation}
      {I have created comprehensive documentation for my projects backend APIs using both Swagger and Postman.}
  \resumeItemListEnd

\resumeSubheading
  {DandD Tech USA Inc.}{Brooklyn, NY, USA}
  {Backend Engineer}{October 2020 - January 2023}
  \resumeItemListStart
  \resumeItem{Projects}
       {Built and Engineered backend APIs for multiple projects such as
       \href{https://robofood.io/}{https://robofood.io/} - A cloud restaurant autopilot.
       \href{https://frontliner.care/}{https://frontliner.care/} / {https://member.ods2.us/}{https://member.ods2.us/} - A complete software platform and EMR that provides superior client outcome, improves caregiver retention, and reduce administrative overhead.}
  \resumeItem{Authentication and Authorization}
      {Integrated Secure Authentication and Authorization: Using Jsonwebtoken , PassportJS, Twilio Verify V2 Service for OTP verfication.}
  \resumeItem{Notification services}
      {Integrated notifications services for email using Twilio with send grid api, and for SMS using Twilio SMS and whatsapp massaging service}
      {Integrated Notification module using twilio api for periodic SMS, mail & whatsapp message notification}
  \resumeItemListEnd

\resumeSubheading
  {Fliqa India Pvt. Ltd}{Bidhannagar, Kolkata, West Bengal}
  {Fullstack Developer}{October 2019 - October 2020}
  \resumeItemListStart
  \resumeItem{Projects}
       {Built the Full stack (MERN) website for
       \href{https://fliqaindia.com/}{https://fliqaindia.com/} - Professional Photography and creative platform.
       I utilized Node.js as the development environment, JavaScript as programming languages, Express.js library for building APIs.
       }
       \resumeItem{Landing Website and Admin Panel}
       {Using MERN stack i have build the landing page along with admin panel which handles Bookings, Leads, CRM, Transactions and many other modules }
  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Tripinnov \href{https://tripinnov.com/}{https://www.tripinnov.com}}
      {A Multi tenant multi portal tech travel subscription and commission based platform for creating and selling travel quotation on the go}
    \resumeSubItem{Ordercoro \href{https://ordercoro.com/}{https://www.ordercoro.com}}
      {A Multiple role ad location based food ordering and order management system open for restaurant owners, vendor, supplier and customers }
    \resumeSubItem{Robofood \href{https://robofood.io/}{https://www.robofood.io}}
      {Manage your restaurant functions like online ordering, billing, CRM, inventory management, centralized menu management}
    \resumeSubItem{Frontliner \href{https://frontliner.care/}{https://www.frontliner.care}}
      {A tech platform for caregiver and patient where caregiver is assigned to patients for helping and caring patient and paid accordingly}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages:} {Javascript, TypeScript.}
    \resumeSubItem{Technologies:} {React.js, Next.js, RESTful APIs, Node.js, Express.js, Nest.js. Twilio, PhonePe, Stripe, and many others}
    \resumeSubItem{Databases:} {Mongodb, PostgressQL.}
    \resumeSubItem{Devops:} {Git, Github, CI/CD, Nginx, PM2, AWS, S3, Digital Ocean, Docker.}
    \resumeSubItem{Soft/Other Skills:} {Agile/Scrum, Problem Solving, Communication, Time Management.}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
