\documentclass[11pt, a4paper]{article}

\usepackage[margin=0.9in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

\pagenumbering{gobble}
\setlist[itemize]{left=0pt, label=--, itemsep=2pt, topsep=3pt}

\begin{document}

% -------------------- HEADER --------------------
\begin{center}
    {\LARGE \textbf{Pulkit Singh}} \\[4pt]
    \href{mailto:pulkitsinghmail@gmail.com}{pulkitsinghmail@gmail.com} \,|\, +91-6294872159 \,|\,
    \href{https://www.linkedin.com/in/pulkit5ingh/}{linkedin.com/in/pulkit5ingh} \,|\,
    \href{https://github.com/pulkit5ingh}{github.com/pulkit5ingh}
\end{center}

% -------------------- SUMMARY --------------------
\section*{Summary}
Senior Backend / Fullstack Developer with 5+ years building \textbf{B2B SaaS} products with complex workflows and user roles. Strong ownership of \textbf{Node.js}, \textbf{TypeScript}, and \textbf{NestJS} for APIs, data models, and integrations; experienced with \textbf{PostgreSQL} (schema design, migrations), \textbf{React}, and \textbf{AWS}. Skilled in authentication, authorisation, and \textbf{RBAC}; comfortable designing and evolving core backend services and collaborating with frontend and product on end-to-end features. Focus on reliability, performance, and maintainability; practised in peer review, test automation, and secure coding. Worked in small, distributed teams with direct impact on architecture and product direction.

% -------------------- TECHNICAL SKILLS --------------------
\section*{Technical Skills}
\textbf{Languages:} TypeScript, JavaScript (ES6+) \\
\textbf{Backend:} Node.js, NestJS, Express.js \\
\textbf{Frontend:} React.js, Next.js \\
\textbf{Databases:} PostgreSQL, MongoDB, Redis (schema design, migrations, aggregations) \\
\textbf{Auth \& Security:} JWT, PassportJS, RBAC, OAuth, OTP-based auth; experience with SSO concepts and third-party integrations \\
\textbf{APIs \& Integrations:} RESTful APIs, webhooks, payment gateways (Razorpay, PhonePe, Easebuzz), external service integrations \\
\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Docker, Nginx, PM2, CI/CD (GitHub Actions, Jenkins) \\
\textbf{Architecture:} Multi-tenant SaaS, microservices, event-driven systems \\
\textbf{Quality \& Ops:} Jest, Mocha, Postman, Swagger; code review, secure coding, log management, performance tuning

% -------------------- EXPERIENCE --------------------
\section*{Experience}

\textbf{Senior Backend Engineer} \hfill \textit{Corpusvision Technologies Pvt. Ltd.} \\
\textit{Feb 2023 -- Present} \\
Mumbai, Maharashtra (Hybrid)
\begin{itemize}
  \item Own and evolve core backend building blocks and APIs for multiple B2B SaaS platforms using \textbf{NestJS} and \textbf{TypeScript}; design and maintain data models and integrations as product needs change.
  \item Implemented scalable \textbf{RBAC} and authentication (PassportJS, JWT) with dynamic permission management; designed authorisation flows for complex user roles and workflows.
  \item Built and maintained integrations (payment gateways via webhooks, PDF generation, Email/SMS); ensured reliability and observability of backend services.
  \item Collaborated with frontend on end-to-end features; contributed to architectural decisions balancing delivery speed and long-term maintainability.
  \item Managed \textbf{AWS} (S3, deployments), Docker, Nginx, and CI/CD; improved platform reliability and operational robustness.
  \item Participated in planning, estimation, and prioritisation; upheld code quality through peer reviews, test automation, and secure coding practices.
\end{itemize}

\\[6pt]

\textbf{Backend Engineer} \hfill \textit{DandD Tech USA Inc.} \\
\textit{Oct 2020 -- Jan 2023} \\
Brooklyn, NY (Remote)
\begin{itemize}
  \item Delivered scalable REST APIs for \textbf{B2B SaaS} (restaurant and healthcare EMR) using Express.js and MongoDB; designed data models and modules for POS, inventory, delivery, booking, and order tracking.
  \item Implemented \textbf{authentication} (Firebase Auth, Twilio OTP); worked across service boundaries on full request and data flows.
  \item Automated reporting and user alerts via scheduled jobs; worked in a small, distributed team with ownership of backend outcomes.
\end{itemize}

\\[6pt]

\textbf{Fullstack Developer} \hfill \textit{Fliqa India} \\
\textit{Jan 2020}
\begin{itemize}
  \item Built full-stack product (Node.js, React, Express, MongoDB): landing site and admin panel for content and operations; Cloudinary for media, Cloudflare for hosting.
\end{itemize}

% -------------------- PROJECTS --------------------
\section*{Projects}
\textbf{Tripinnov} (\href{https://tripinnov.com}{tripinnov.com}) – Travel SaaS for agents: itineraries, quotations, commissions. NestJS backend; complex roles and workflows. \\[4pt]
\textbf{Ordercoro} (\href{https://ordercoro.com}{ordercoro.com}) – Multi-role B2B foodtech (restaurants, vendors, delivery); APIs and integrations. \\[4pt]
\textbf{TravelBaba.ai} (\href{https://travelbaba.ai}{travelbaba.ai}) – AI-powered assistant for travel agents; NestJS, Claude AI; JSON validation and sequencing logic. \\[4pt]
\textbf{Robofood} (\href{https://robofood.io}{robofood.io}) – Restaurant SaaS: POS, billing, inventory, delivery APIs. \\[4pt]
\textbf{Frontliner} (\href{https://frontliner.care}{frontliner.care}) – Healthcare EMR and staffing platform; patient-caregiver workflows. \\[4pt]
\textbf{Quiksale} (\href{https://quiksale.in}{quiksale.in}) – Hyperlocal platform with subscription system and referral tracking. \\[4pt]
\textbf{ShiftPro} – On-demand labour platform for merchants (B2B): location-based discovery, recurring bookings, verified helpers, secure payments. \\[4pt]
\textbf{BakBak} (\href{https://bakbakindia.com}{bakbakindia.com}) – Hyperlocal platform: social feed, local services, civic issues (Mudda), voice-first interaction. \\[4pt]
\textbf{Fliqa India} (\href{https://fliqaindia.com}{fliqaindia.com}) – Full-stack MERN site and admin panel; React, Node.js, Cloudinary, Cloudflare. \\[4pt]

% -------------------- EDUCATION --------------------
\section*{Education}
\textbf{Institute of Science and Technology}, Chandrakona, West Bengal \\
Bachelor of Computer Applications (BCA), 2017 -- 2020 \\[4pt]
\textbf{S.E. Rly Mixed Higher Secondary School}, Kharagpur, West Bengal \\
Higher Secondary and Secondary, 2012 -- 2017

\end{document}
