\documentclass[11pt, a4paper]{article}

\usepackage[margin=0.9in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

\pagenumbering{gobble}
\setlist[itemize]{left=0pt, label=--, itemsep=2pt, topsep=3pt}

\begin{document}

% -------------------- HEADER --------------------
\begin{center}
    {\LARGE \textbf{Pulkit Singh}} \\[4pt]
    \href{mailto:pulkitsinghmail@gmail.com}{pulkitsinghmail@gmail.com} \,|\, +91-6294872159 \,|\,
    \href{https://www.linkedin.com/in/pulkit5ingh/}{linkedin.com/in/pulkit5ingh} \,|\,
    \href{https://github.com/pulkit5ingh}{github.com/pulkit5ingh}
\end{center}

% -------------------- SUMMARY --------------------
\section*{Summary}
Senior Backend Engineer with 5+ years of experience developing scalable, high-performance RESTful and microservice-based architectures using \textbf{Node.js}, \textbf{NestJS}, and \textbf{TypeScript}. Skilled in designing secure APIs, Role-Based Access Control (RBAC) systems, and asynchronous task processing with \textbf{BullMQ} and \textbf{Redis}. Strong background in containerized, multi-tenant B2B SaaS applications hosted on \textbf{Google Cloud Platform (GCP)} and \textbf{AWS}, focusing on scalability, resilience, and cost efficiency. Experienced with API performance optimization, serverless architectures (\textbf{AWS Lambda}), and deployments using \textbf{Docker}, \textbf{Nginx}, and \textbf{Kubernetes}. Proficient in building CI/CD pipelines (\textbf{GitHub Actions}, \textbf{Jenkins}) and managing cloud infrastructure. Adept at developing real-time systems using \textbf{WebSockets} and message queues (\textbf{Kafka}, \textbf{BullMQ}), ensuring secure and fault-tolerant backend systems for enterprise environments.

% -------------------- TECHNICAL SKILLS --------------------
\section*{Technical Skills}
\textbf{Languages:} JavaScript (ES6+), TypeScript \\
\textbf{Backend Frameworks:} Node.js, Express.js, NestJS \\
\textbf{Frontend (Basic):} React.js, Next.js \\
\textbf{Databases:} MongoDB, PostgreSQL, Redis \\
\textbf{Architecture \& Design:} Microservices, RESTful APIs, Multi-Tenant SaaS, Event-Driven Systems \\
\textbf{DevOps \& Cloud:} Docker, Kubernetes, Google Cloud Platform (GCP), AWS (EC2, S3, Lambda), DigitalOcean (Droplets, App Platform), Nginx, PM2, CI/CD (GitHub Actions, Jenkins) \\
\textbf{AI Development Tools:} Claude AI (Anthropic SDK), Cursor, Codeium, Antigravity Cursor \\
\textbf{Messaging \& Queues:} BullMQ, Kafka, RabbitMQ \\
\textbf{Testing \& QA:} Jest, Mocha, Postman, Swagger \\
\textbf{Monitoring \& Optimization:} Log Management, API Performance Tuning, Caching Strategies, Scalability Engineering \\
\textbf{Version Control \& Collaboration:} Git, GitHub, Agile, Scrum

% -------------------- EXPERIENCE --------------------
\section*{Experience}

\textbf{Senior Backend Engineer} \hfill \textit{Corpusvision Technologies Pvt. Ltd.} \\
\textit{Feb 2023 -- Present} \\
Mumbai, Maharashtra (Hybrid)
\begin{itemize}
  \item \textbf{Backend Architecture:} Designed and developed robust APIs for multiple platforms using NestJS and TypeScript.
  \item \textbf{Role-Based Access Control (RBAC):} Implemented scalable RBAC system using PassportJS and JWT, enabling dynamic permission management.
  \item \textbf{Bulk Upload System:} Built an Excel-based bulk upload engine with validation, transformation, and feedback mechanisms using BullMQ and Redis.
  \item \textbf{Analytics \& Reporting:} Leveraged MongoDB aggregation pipelines to generate real-time admin and user reports.
  \item \textbf{Payment Gateway Integrations:} Integrated Razorpay, PhonePe, and Easebuzz via webhooks, supporting subscriptions and transactional workflows.
  \item \textbf{PDF \& Notification Automation:} Automated generation of OTPs, invoices, and quotations with templated PDFs and multi-channel notifications (Email/SMS).
  \item \textbf{Infrastructure Management:} Managed deployments with Docker, PM2, and Nginx. Configured AWS S3 for secure file handling and CI/CD pipelines.
\end{itemize}

\\[6pt]

\textbf{Backend Engineer} \hfill \textit{DandD Tech USA Inc.} \\
\textit{Oct 2020 -- Jan 2023} \\
Brooklyn, NY (Remote)
\begin{itemize}
  \item \textbf{API Development:} Delivered scalable REST APIs for restaurant SaaS and healthcare EMR platforms using Express.js and MongoDB.
  \item \textbf{Module Design:} Implemented modules for POS, inventory, delivery, booking, and order tracking.
  \item \textbf{Automation:} Scheduled CRON jobs for reporting and user alerts.
  \item \textbf{Authentication:} Enabled secure login via Firebase Auth and Twilio for OTP-based access.
\end{itemize}

\\[6pt]

\textbf{Fullstack Developer} \hfill \textit{Fliqa India} \\
\textit{Jan 2020 -- Jan 2020}
\begin{itemize}
  \item Built the full-stack (MERN) website for \href{https://fliqaindia.com}{Fliqa India} — professional photography and creative platform. Utilized Node.js, React.js, Express.js, and MongoDB; Cloudinary for image and video storage; Cloudflare for hosting.
  \item Built the landing page and admin panel for content and operations management.
\end{itemize}

% -------------------- PROJECTS --------------------
\section*{Projects}
\textbf{TravelBaba.ai} (\href{https://travelbaba.ai}{travelbaba.ai}) – AI-powered assistant for travel agents to generate instant itineraries and quotations using Claude AI (Anthropic SDK) with NestJS backend. Implemented strict JSON validation and sequencing logic for multi-day itineraries. \\[4pt]
\textbf{Quiksale} (\href{https://quiksale.in}{quiksale.in}) – Hyperlocal resale platform with geolocation filtering, referral tracking, and subscription system. \\[4pt]
\textbf{Tripinnov} (\href{https://tripinnov.com}{tripinnov.com}) – Travel SaaS for agents to manage itineraries, generate quotations, and track commissions. \\[4pt]
\textbf{Ordercoro} (\href{https://ordercoro.com}{ordercoro.com}) – Multi-role foodtech ecosystem connecting restaurants, vendors, and delivery services. \\[4pt]
\textbf{Robofood} (\href{https://robofood.io}{robofood.io}) – Cloud kitchen autopilot with POS, billing, inventory, and delivery APIs. \\[4pt]
\textbf{ShiftPro} – Mumbai's first on-demand hourly labour platform for merchants and businesses. Dual-sided marketplace: merchant app for hiring helpers by the hour (packing, loading, cleaning, delivery) with location-based discovery, transparent pricing, and recurring bookings; helper app for profiles, multi-service listings, and earnings. Built with verified helpers, ratings, and secure payments. \\[4pt]
\textbf{BakBak} (\href{https://bakbakindia.com}{bakbakindia.com}) – India's hyperlocal platform for local life: social feed by neighborhood, discovery of trusted local services (plumbers, tutors, etc.), civic issue-raising (Mudda) with community voting, and voice-first interaction. Combines social connectivity with hyperlocal governance and local business presence (BakBak Ki Dukaan). \\[4pt]
\textbf{Frontliner} (\href{https://frontliner.care}{frontliner.care}) – Healthcare EMR and staffing platform for patient-caregiver management. \\[4pt]
\textbf{Fliqa India} (\href{https://fliqaindia.com}{fliqaindia.com}) – Professional photography and creative platform. Full-stack MERN website with landing page and admin panel; Node.js, React.js, Express.js, MongoDB, Cloudinary for media, Cloudflare for hosting. \\[4pt]

% -------------------- EDUCATION --------------------
\section*{Education}
\textbf{Institute of Science and Technology}, Chandrakona, West Bengal \\
Bachelor of Computer Applications (BCA), 2017 -- 2020 \\[4pt]
\textbf{S.E. Rly Mixed Higher Secondary School}, Kharagpur, West Bengal \\
Higher Secondary and Secondary, 2012 -- 2017

\end{document}
